---
title: "evogeno Project"
author: "Sophia Halling,"
date: "2024-04-22"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract

# 1-2 paragraph motivating reasons

# 2-3 paragraph introduction

#Methods

## libraries

```{r}
library(tidyverse)
library(knitr)
library(plotly)
```

## Neon table setup

### NEON table
```{r}
NEON_MAGs <- read_csv("data/NEON/GOLD_Study_ID_Gs0161344_NEON_edArchaea.csv") %>% 
  # remove columns that are not needed for data analysis
  select(-c(`GOLD Study ID`, `Bin Methods`, `Created By`, `Date Added`)) %>% 
  # create a new column with the Assembly Type
  mutate("Assembly Type" = case_when(`Genome Name` == "NEON combined assembly" ~ `Genome Name`,
                            TRUE ~ "Individual")) %>% 
  mutate_at("Assembly Type", str_replace, "NEON combined assembly", "Combined") %>% 
  separate(`GTDB-Tk Taxonomy Lineage`, c("Domain", "Phylum", "Class", "Order", "Family", "Genus"), "; ", remove = FALSE) %>% 
  # Get rid of the the common string "Soil microbial communities from "
  mutate_at("Genome Name", str_replace, "Terrestrial soil microbial communities from ", "") %>% 
  # Use the first `-` to split the column in two
  separate(`Genome Name`, c("Site","Sample Name"), " - ") %>% 
  # Get rid of the the common string "S-comp-1"
  mutate_at("Sample Name", str_replace, "-comp-1", "") %>%
  # separate the Sample Name into Site ID and plot info
  separate(`Sample Name`, c("Site ID","subplot.layer.date"), "_", remove = FALSE,) %>% 
  # separate the plot info into 3 columns
  separate(`subplot.layer.date`, c("Subplot", "Layer", "Date"), "-") 
```

### NEON metagenome table

```{r}
NEON_metagenomes <- read_tsv("data/NEON/exported_img_data_Gs0161344_NEON.tsv") %>% 
  rename(`Genome Name` = `Genome Name / Sample Name`) %>% 
  filter(str_detect(`Genome Name`, 're-annotation', negate = T)) %>% 
  filter(str_detect(`Genome Name`, 'WREF plot', negate = T)) 
```

```{r}
NEON_metagenomes <- NEON_metagenomes %>% 
  # Get rid of the the common string "Soil microbial communities from "
  mutate_at("Genome Name", str_replace, "Terrestrial soil microbial communities from ", "") %>% 
  # Use the first `-` to split the column in two
  separate(`Genome Name`, c("Site","Sample Name"), " - ") %>% 
  # Get rid of the the common string "-comp-1"
  mutate_at("Sample Name", str_replace, "-comp-1", "") %>%
  # separate the Sample Name into Site ID and plot info
  separate(`Sample Name`, c("Site ID","subplot.layer.date"), "_", remove = FALSE,) %>% 
  # separate the plot info into 3 columns
  separate(`subplot.layer.date`, c("Subplot", "Layer", "Date"), "-") 
```

## NEON chemistry table

```{r}
NEON_chemistry <- read_tsv("data/NEON/neon_plot_soilChem1_metadata.tsv") %>% 
  # remove -COMP from genomicsSampleID
  mutate_at("genomicsSampleID", str_replace, "-COMP", "") 
```

Neon 
Img
Sankey
Positcloud
Rmarkdown
filtering methods
Zotero
Pavian
Screenshot of data/graphs and put code chunks in methods

# Results

## Possible question types

Temperature, ecosystem, chemistry, ph

Lab 12 metagenome +chemistry data tables (use Sophia’s exercise 8+)

Question: 
nitrogen% vs. organic C % (E11)

Question: What is the relationship between the organic carbon percentage and nitrogen percentage in relation to bacteriodata families?

Soil temperature vs. soil in cacl pH (E11)

Question: Do soil temperatures and Calcium Chloride pH levels effect bacteropdota families?

Soil in water pH vs. soil in cacl pH (E11)

Question: 

Nlcd class vs. soil in cacl pH (E10)

Question: 


#### Question:How does soil temperature affect the distribution of bacteroides?

##### Graphs
Site vs. temp (all phylums)
soil temp vs. ecosystem

Site id vs. soil temperature(bacteroidota only) (E8)

Soil temp vs. ecosystem (all phylums)
Distribution of various orders in bacteroidota based on soil temperature in different ecosystems (E9)

Lab 15 trees  (not done yet)
Sankey? (into or results?)
Paragraphs talking about what each graph displays

# Discussion
Talk about results and what they mean

# Conclusion
Lab 10
Big picture discussion
References
Zotero 
lab 10/11